---
title: "10_assignment"
author: "Dariusz Dziubinski"
date: "26/08/2023"
format: html
execute:
  echo: fenced
---

<style>
table {
  font-size: 14px;
}
</style>

<div class="figure">
  <p class="caption"></p>
  <img src="https://upload.wikimedia.org/wikipedia/commons/b/bc/Friends_logo.svg" alt="" width="500">
</div>

## **I. TV Series Description**

::: {style="text-align: justify"}
The series narrative follows six friends living and working in New York City: *Rachel Green*, *Monica Geller*, *Phoebe Buffay*, *Joey Tribbiani*, *Chandler Bing*, and *Ross Geller* played by *Jennifer Aniston*, *Courteney Cox*, *Lisa Kudrow*, *Matt LeBlanc*, *Matthew Perry*, and *David Schwimmer* respectively. All episodes were filmed at Warner Bros. Studios, Burbank. The fourth season finale, "The One with Ross's Wedding", however, was filmed on location in London in front of a British studio audience.
:::
 
## **II. Basic statistics**

| Season | Episodes | First aired        | Last aired       | Rank | Rating | Viewers (mln) |
|--------|----------|--------------------|------------------|------|--------|---------------|
| 1      | 24       | September 22, 1994 | May 18, 1995     | 8    | 15.6   | 24.8          |
| 2      | 24       | September 21, 1995 | May 16, 1996     | 3    | 18.7   | 31.7          |
| 3      | 25       | September 19, 1996 | May 15, 1997     | 4    | 16.8   | 26.1          |
| 4      | 24       | September 25, 1997 | May 7, 1998      | 4    | 16.1   | 25.0          |
| 5      | 24       | September 24, 1998 | May 20, 1999     | 2    | 15.7   | 24.7          |
| 6      | 25       | September 23, 1999 | May 18, 2000     | 5    | 14.0   | 22.6          |
| 7      | 24       | October 12, 2000   | May 17, 2001     | 5    | 12.6   | 22.1          |
| 8      | 24       | September 27, 2001 | May 16, 2002     | 1    | 15.0   | 26.4          |
| 9      | 24       | September 26, 2002 | May 15, 2003     | 2    | 13.5   | 23.9          |
| 10     | 18       | September 25, 2003 | May 6, 2004      | 5    | 13.6   | 24.6          |

## **III. Viewership over time**

```{r Viewers (mln), echo=FALSE, warning=FALSE, message=FALSE}
library(ggplot2)

tv_data <- data.frame(
  Season = c(1:10),
  Episodes = c(24, 24, 25, 24, 24, 25, 24, 24, 24, 18),
  First_aired = c("September 22, 1994", "September 21, 1995", "September 19, 1996",
                  "September 25, 1997", "September 24, 1998", "September 23, 1999",
                  "October 12, 2000", "September 27, 2001", "September 26, 2002",
                  "September 25, 2003"),
  Viewers_mln = c(24.8, 31.7, 26.1, 25.0, 24.7, 22.6, 22.1, 26.4, 23.9, 24.6)
)

ggplot(tv_data, aes(x = Season, y = Viewers_mln)) +
  geom_line(color = "blue", group = 1) + 
  geom_point(color = "red") +
  labs(title = "Viewership figures by season",
       x = "Season",
       y = "Viewers (mln)") +
  theme_minimal() +
  scale_x_continuous(breaks = 1:10) +
  scale_y_continuous(breaks = seq(22, 32, by = 1), limits = c(22, 32))

```

## **IV.Viewership by episode in the first season**

```{r Viewers episode (mln), echo=FALSE, warning=FALSE, message=FALSE}
episode_data <- data.frame(
  Episode_No = c(1:24),
  Title = paste("Episode Title", 1:24),
  Viewers_mln = c(21.5, 20.2, 19.5, 19.7, 18.6, 18.2, 23.5, 21.1, 23.1, 19.9, 
                  26.6, 24.0, 25.8, 23.8, 24.8, 26.1, 30.5, 30.4, 29.4, 30.0, 
                  28.4, 29.9, 28.7, 31.3)
)

ggplot(episode_data, aes(x = Episode_No, y = Viewers_mln)) +
  geom_line(color = "blue", group = 1) + 
  geom_point(color = "red") +
  labs(title = "Viewership figures by episode in Season I",
       x = "Episode Number",
       y = "Viewers (mln)") +
  theme_minimal() +
  scale_x_continuous(breaks = 1:24) +
  scale_y_continuous(breaks = seq(min(episode_data$Viewers_mln), max(episode_data$Viewers_mln), by = 1))
```

